Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-19 paper/ms.tex
update text

Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
154 milliangstrom (see attached).

As a reminder, Teff=6100K (TICv8). 
Or Teff = 5946 $\pm$ 39 (CHIRON).
Rafael, if you have a better
determination of Teff, it would be helpful!  SpType is early-G,
late-F from your quicklook spectral typing earlier.

Relevant colors are V-K = 1.7,  V-I ~= V-T = 0.7

Summarizing relevant lithium facts:

@@

Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
Hyads shows that the depletion does happen over gigayear timescales
(Berger+2018, fig 7).

Comparing to the Li EWs measured by Berger+2018 (their Fig 5),
TOI-837 is consistent with being younger than almost all CKS
planet-hosting field stars.

The TOI-837 Li EW measured here (150 milliangstrom) is consistent
with what's seen for stars of similar colors in <100 Myr old moving
groups (Elliott+2016, Fig 11 -- attached).  This is sensible, because
IC 2602 is supposed to be 50 Myr old.

@@

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}.
 	{\it Imaging}:
  Second Generation Digitized Sky Survey,
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	{\it Spectroscopy}:
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
% 	El Sauce:0.356m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
% 	NTT,
% 	SOAR (SOI),
 	TESS \citep{ricker_transiting_2015}.
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
}

>>>>

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Lithium 6708\AA\ equivalent widths for \tn, field stars, and
    young open clusters.}
    The field star sample is drawn from Kepler planet hosts,
    and was measured by
    \citet{berger_identifying_2018} using Keck-HIRES.
    The young open clusters members were surveyed by
    \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
    spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018}
    found lithium depletion boundary ages for these clusters of
    $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
    $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).
    \label{fig:lithium}
	}
\end{figure}

Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
154 milliangstrom.

@@

Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
Hyads has shown that the depletion does happen over gigayear timescales
(Berger+2018, fig 7).

Figure~\ref{fig:lithium} compares our measured \tn\ Li EW 
to stars in the field, and to young open cluster members.
The field star measurements were collected by
\citet{berger_identifying_2018}.
We have shown the points with lithium detections at ${\rm SNR}>3$.
TOI-837 is consistent with being younger than almost all CKS
planet-hosting field stars.

The young open cluster members were selected for the presence of
lithium, as described by \citet{randich_gaiaeso_2018}.
The TOI-837 Li EW measured here (150 milliangstrom) is consistent
with what's seen for stars of similar colors in <100 Myr old moving
groups.
(Elliott+2016, Fig 11 -- attached).  This is sensible, because
IC 2602 is supposed to be 50 Myr old.

@@

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}.
 	{\it Imaging}:
  Second Generation Digitized Sky Survey,
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	{\it Spectroscopy}:
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
 	{\bf VLT (number), UVES and GIRAFFE} (CITE: Pasquini et al 2002)
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
% 	El Sauce:0.356m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
% 	NTT,
% 	SOAR (SOI),
 	TESS \citep{ricker_transiting_2015}.
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
}
